\sysfull

### 2018-04-17 paper/intro.tex
abstract, and had to move figures to fix layout
introduction typo

%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
\textbf{Challenges.} While a compiler can use static data privatization and commit instrumentation
(i.e., redo-logging) to eliminate statically identifiable, inter-task data
dependences~\citep{alpaca}, a \emph{dynamic} dependence between two coalesced
tasks requires dynamic privatization and commit actions. 
%
To ensure consistency and respect inter-task dependences, \sys uses a novel
approach \emph{power failure immune memory virtualization} that buffers non-volatile variable
updates in volatile memory during a coalesced task execution, before committing
them to non-volatile memory at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.
A static task decomposition model assumes that each
single task can execute to completion. If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. To avoid non-termination under adversarial
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial execution avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted. Partial execution violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial execution around a piece of code.
%
% !!!! % It should be emphasized that unlike a voltage-threshold-based protection approaches that may suffer from a non-termination problem if the checkpoint has to be placed within the interrupt-disabled region, a timer-based approach adapts its partial commit location on repeated failures. 
%
%Task coalescing removes the burden from the programmer, because it accepts any
%task decomposition and improves it dynamically. To further reduce the
%programmer effort, we propose a compiler pass for \emph{automatic
%decomposition} of programs into (small) \emph{atomic} tasks. The compiler
%identifies non-volatile variables shared across tasks as tasks are created, and
%instruments reads and writes of those variables, using memory virtualization,
%to keep the data consistent in the presence of power loss.
%
%\textcolor{red}{Despite being limited to a subset of the C language, the
%automatic task decomposition allowed us to port several	applications to an
%intermittent platform with a moderate effort.}
%

>>>>

%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
\textbf{Challenges.} While a compiler can use static data privatization and commit instrumentation
(i.e., redo-logging) to eliminate statically identifiable, inter-task data
dependences~\citep{alpaca}, a \emph{dynamic} dependence between two coalesced
tasks requires dynamic privatization and commit actions. 
%
To ensure consistency and respect inter-task dependences, \sys uses a novel
approach \emph{power failure-immune memory virtualization} that buffers non-volatile variable
updates in volatile memory during a coalesced task execution, before committing
them to non-volatile memory at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.
A static task decomposition model assumes that each
single task can execute to completion. If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. To avoid non-termination under adversarial
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial execution avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted. Partial execution violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial execution around a piece of code.
%
% !!!! % It should be emphasized that unlike a voltage-threshold-based protection approaches that may suffer from a non-termination problem if the checkpoint has to be placed within the interrupt-disabled region, a timer-based approach adapts its partial commit location on repeated failures. 
%
%Task coalescing removes the burden from the programmer, because it accepts any
%task decomposition and improves it dynamically. To further reduce the
%programmer effort, we propose a compiler pass for \emph{automatic
%decomposition} of programs into (small) \emph{atomic} tasks. The compiler
%identifies non-volatile variables shared across tasks as tasks are created, and
%instruments reads and writes of those variables, using memory virtualization,
%to keep the data consistent in the presence of power loss.
%
%\textcolor{red}{Despite being limited to a subset of the C language, the
%automatic task decomposition allowed us to port several	applications to an
%intermittent platform with a moderate effort.}
%
